Simulation of Congenital Heart Defect Corrective Surgeries Using Thin Shell Elements

### 2012-03-01 Doc/Miccai/introduction.tex
shell model
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@374 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

%In this paper we present an improved approach using a simulation model solely based on elastic thin shell elements. Our method is not limited to well-formed blood vessels and captures all low-level procedures necessary for aortoplasty. By using a relaxation process we can arbitrarily join or attach blood vessels and patches without using springs that would add surplus energy to the physical system. We prove that simulation time is still reasonable or even decreased by taking special care of the overall tubular structure of blood vessels during generation of thin shell elements.
We improve the capabilities of the simulation by using a model based on elastic thin shell elements.
This allows us to model arbitrary blood vessels and malformations of the artery.
It can also capture all low-level procedures necessary for aortoplasty.
By using a relaxation process we can arbitrarily join or attach blood vessels and patches without using springs that would add surplus energy to the physical system.
\tomas{I don't think this is correct: (}
We prove that simulation time is still reasonable or even decreased by taking special care of the overall tubular structure of blood vessels during generation of thin shell elements.
\tomas{) we don't make any speed comparison. I propose this: }
By taking into consideration the overall tubular structure of blood vessels during generation of thin shell elements we can still maintain reasonable speed of the simulation.
\tomas{)}

>>>>

%In this paper we present an improved approach using a simulation model solely based on elastic thin shell elements. Our method is not limited to well-formed blood vessels and captures all low-level procedures necessary for aortoplasty. By using a relaxation process we can arbitrarily join or attach blood vessels and patches without using springs that would add surplus energy to the physical system. We prove that simulation time is still reasonable or even decreased by taking special care of the overall tubular structure of blood vessels during generation of thin shell elements.
We improve the capabilities of the simulation by using a model based on elastic thin shell elements.
This allows us to model arbitrary blood vessels and malformations of the artery.
It can also capture all low-level procedures necessary for aortoplasty.
By using a relaxation process we can arbitrarily join or attach blood vessels and patches without using springs that would add surplus energy to the physical system.
\tomas{I don't think this is correct: (}
We prove that simulation time is still reasonable or even decreased by taking special care of the overall tubular structure of blood vessels during generation of thin shell elements.
\tomas{) we don't make any speed comparison. I propose this: }
By taking into consideration the overall tubular structure of blood vessels during generation of thin shell elements we can still maintain rereal-time speed of the simulation.
\tomas{)}

### 2012-03-01 Doc/Miccai/shell-model.tex
Added paragraph break...
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@371 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b
shell model
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@374 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

In congenital heart defect (CHD) corrective surgeries blood vessels respond to plastic interventions with a certain amount of deformation. Surgeons try to find an optimal approach to correct defects with a minimum of deformations and collisions that would have unnecessary negative impact on blood flow or that may lead to problems during growth of the patient. To be able to predict results for different surgical approaches a physical approriate model of blood vessels is mandatory. Furthermore, computation time of simulations must be low enough to enable interactive and usable planning software. Options on the choice of model are limited. Mass-spring models allow for fast computation but do not correlate to a physical accurate representation of reality and therefore are inappropriate for predictive simulations. On the contrary, simulation models based on the formulation of finite elements, either 3-dimensional elements or thin shell elements, are commonly used when high physical accuracy is required but are well known to be computationally expensive. The hybrid blood vessel model of \cite{Li2009} strikes a balance but is too constrained to be used as a truly universal approach for all kinds of surgical procedures used in CHD corrective surgery. We propose a model based on thin shell elements that still allows for fast computation with a reasonable number of elements.

>>>>

In congenital heart defect (CHD) corrective surgeries blood vessels respond to plastic interventions with a certain amount of deformation. Surgeons try to find an optimal approach to correct defects with a minimum of deformations and collisions that would have unnecessary negative impact on blood flow or that may lead to problems during growth of the patient. To be able to predict results for different surgical approaches a physicaly approriate model of blood vessels is mandatory. Furthermore, computation time of simulations must be low enough to enable interactive and usable planning software.

Options on the choice of model are limited. Mass-spring models, often used for cloth simulation \cite{Volino2005b}, allow for fast computation but do not do not posses the required level of physical accuracy and therefore are inappropriate for predictive simulations. On the contrary, simulation models based on the formulation of finite elements, either 3-dimensional elements or thin shell elements, are commonly used when high physical accuracy is required but are well known to be computationally expensive \tomas{add some refs?}. The hybrid blood vessel model of \cite{Li2009} strikes a balance but is too constrained to be used as a truly universal approach for all kinds of surgical procedures used in CHD corrective surgery. We propose a model based on thin shell elements that still allows for fast computation with a reasonable number of elements.

\tomas{I'm adding this back, the previous focuess only on physical correctnes.}
Apart from physical accuracy the model should provide 
(I) a good support for the deformations by bending and twisting,
(II) an accurate modeling of the wall motion when the vessel is cut along its axis,
(III) global deformations of stitched vessels that capture their final configuration, after surgery,
(IV) collision response when detected (e.g. between the aortic arch and pulmonary artery).
All these requirements are fullfilled by the shell element model.
